Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2014-12-14 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] cleaned up scalar operator section, comparing with lit, other small changes

We will also make use of the branching ratio of $B\to K^* \bar\mu\mu$ as it
allows us to $\ldots$
\todo{$A_{\rm CP}$ included.}

\todo{Find a place to cite \cite{Becirevic:2012fy}, perhaps in section on results
comparing our bounds to theirs in eq.(49): $|\wilson{S,\,S'}|Ê\lesssim 0.7$ and
$|\wilson{P,\,P'}|Ê\lesssim 1.0$ - what about \cite{Altmannshofer:2012az}
and \cite{Hurth:2012jn, Hurth:2013ssa} (this is only MFV, i.e. only one operator)?}.

In our fit of the effective couplings $\wilson{i}(\mu_b)$, we do not neglect
kinematically suppressed terms in observables, neither in the prediction of
yet not measured observables. The experimental input of these observables is 
listed in \reftab{tab:observables} together with input for the $B\to K^{(*)}$
form factors. More details on the latter can be found in \refapp{app:theory:inputs}.

@@

@@

The SM gauge groups do not impose constraints on the operators of the SM-EFT that
imply relations among $\wilson{10}$ and $\wilson{10'}$, so they
are in general additional independent parameters. Here we find that destructive
interference with contributions involving $\wilson{10,\, 10'}$ do not change
much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. However,
for the most general case of complex-valued couplings destructive interference
constrains (4 parameters)

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
  \caption{
    \eos{
    Constraints on real-valued [left] and complex-valued [right] scalar couplings 
    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to 
    \bar\mu\mu)$ (blue) and 
    all data in \reftab{tab:observables} (green) marginalising over non-zero 
    $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and 
    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$, 
    or all data but $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
    at 68\% (darker) and 95\% (lighter) probability. 
    }
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

@@

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensorial couplings \eos{$|{\cal C}_{T,\,T5}^\mu|
  < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\, 
  (0.45)$}, even in the presence of non-standard contributions in vectorial
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar 
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vectorial couplings
  \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
  0.1\, (0.2)$} for $i = S,P$. Currently, the bounds from $F_H^\mu$ are not as
  strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by a factor four.
  Future measurements at LHCb and Belle II might change this, especially for 
  $\ell = e$. 
\item SM-EFT $\ldots$
\end{enumerate}
In all cases these \eos{constraints are weakened only slightly} in the presence of
new physics in vectorial couplings from destructive interference.

>>>>

Eventually we also explore the behaviour of derived constraints with respect
to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
this purpose we include also the branching ratio and the rate CP asymmetry
of $B\to K^* \bar\mu\mu$ as it provides additional constraints on the moduli
of vectorial couplings.

In our fit of the effective couplings $\wilson{i}(\mu_b)$, we do not neglect
kinematically suppressed terms in predictions of measured observables as well
as when predicting not yet measured observables. The experimental input of these
observables is listed in \reftab{tab:observables} together with input for the 
$B\to K^{(*)}$ form factors. More details on the latter can be found in 
\refapp{app:theory:inputs}.

@@

Our results improve and extend previous constraints in the literature to
the most general case of complex-valued couplings. For example they are
a factor \eos{two to three} more stringent then \cite{Becirevic:2012fy} and
\eos{comparable} to \cite{Altmannshofer:2012az} once restricting to scenarios
considered there.

@@

The SM gauge groups do not impose constraints on the operators of the SM-EFT that
imply relations among $\wilson{10}$ and $\wilson{10'}$, so they
are in general additional independent parameters. Here we find that destructive
interference with contributions involving $\wilson{10,\, 10'}$ do not change
much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. However,
for the most general case of complex-valued couplings destructive interference
constrains (4 parameters) \todo{finish, describe \reffig{fig:scalar:SM-EFT}}

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
  \caption{
    \eos{
    Constraints on real-valued [left] and complex-valued [right] scalar couplings 
    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to 
    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green) 
    at 68\% (darker) and 95\% (lighter) probability when marginalising
    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and 
    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
    For comparison the according constraints from all data when keeping
    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
    at 68\% (darker) and 95\% (lighter) probability. 
    }
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|cc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & NP
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  & $[15,\, 19]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  & $[15,\, 19]$
  & $[ ,\, ]$ ($[ ,\, ]$) 
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  & $[15,\, 19]$
  & $[ ,\, ]$ ($[ ,\, ]$) 
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:predictions}
     \todo{predictions for $B\to K^*\bar\ell\ell$}
  }
\end{table*}

@@

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensorial couplings \eos{$|{\cal C}_{T,\,T5}^\mu|
  < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\, 
  (0.45)$}, even in the presence of non-standard contributions in vectorial
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar 
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vectorial couplings
  \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
  0.1\, (0.2)$} for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds 
  from $F_H^\mu$ are not as strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$
  by a factor four. In the future, measurements at LHCb and Belle II will 
  further tighten the bounds. Moreover, measurements of $F_H^e$ ($\ell = e$)
  will provide constraints on scalar couplings in the electron channel in
  the lack of measurements of $B_s \to \bar{e}e$. 
\item SM-EFT $\ldots$
\end{enumerate}
In all cases these \eos{constraints are weakened only slightly} in the presence of
new physics in vectorial couplings from destructive interference.
